---
title: "Geography 176A Labs"
author: "[Tiago] (https:/TiagoSchwartz.github.io)"
date: 08/13/20
subtitle: "Lab 02"
output:
  html_document:
    theme: darkly
---  
```{r}
library (tidyverse)
library(dplyr)
library(zoo)
library(knitr)
library(readr)
coviddata=read.csv("https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-counties.csv")

```

"Question 1"
```{r}
 coviddata %>%
    filter(date == max(date), state=="California") %>%
    slice_max(cases, n = 5)
```
```{r}

```



 
The table above shows the counties in California with the most current cases of Covid-19

The table below shows the counties in California with the most cumulative cases   

```{r}
coviddata%>%
  filter(state=="California") %>% 
  group_by(county) %>%
  summarize(sumCases=sum(cases)) %>% 
  slice_max(sumCases, n=5)
```




And these are the 5 safest counties in California as of today

 
```{r}
coviddata %>%
    filter(date == max(date), state=="California") %>%
    slice_min(cases, n = 5)

```




"Question 2"
In this question, we are going to look at the story of 4 states and the impact scale can have on data interprtation. The states include: New York, California, Louisiana, and Florida.

Your task is to make a faceted bar plot showing the number of daily, new cases at the state level.

```{r}
coviddata%>%
    filter(state=="California") %>% 
    summarize(sumCases=sum(cases)) %>% 
    slice_max(sumCases) %>% 
    ggplot(aes(x ="", y = sumCases))+
    geom_col(fill = "darkred", color = "darkred", alpha = .25) +
    labs(title = "Total Cases in the California",
         x = "California",
         y = "Cases",
         subtitle = 'NY Times',
         color = "",
         size = "Population") 
  
  coviddata%>%
    filter(state=="New York") %>% 
    summarize(sumCases=sum(cases)) %>% 
    slice_max(sumCases) %>% 
    ggplot(aes(x ="", y = sumCases))+
    geom_col(fill = "darkblue", color = "darkblue", alpha = .25) +
    labs(title = "Total Cases in the New York",
         x = "New York",
         y = "Cases",
         subtitle = 'NY Times',
         color = "",
         size = "Population") 
  
  coviddata%>%
    filter(state=="Florida") %>% 
    summarize(sumCases=sum(cases)) %>% 
    slice_max(sumCases) %>% 
    ggplot(aes(x ="", y = sumCases))+
    geom_col(fill = "orange", color = "darkblue", alpha = .25) +
    labs(title = "Total Cases in the Florida",
         x = "Florida",
         y = "Cases",
         subtitle = 'NY Times',
         color = "",
         size = "Population") 
  
  coviddata%>%
    filter(state=="Louisiana") %>% 
    summarize(sumCases=sum(cases)) %>% 
    slice_max(sumCases) %>% 
    ggplot(aes(x ="", y = sumCases))+
    geom_col(fill = "darkgreen", color = "darkblue", alpha = .25) +
    labs(title = "Total Cases in the Louisiana",
         x = "Louisiana",
         y = "Cases",
         subtitle = 'NY Times',
         color = "",
         size = "Population") 

```





